Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
updated fig 11
remove small-deformation
updated title

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[aps,prl,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}

@@

\title{Vesicle-vesicle adhesion in linear flows: dynamics and rheology}% Force line breaks with \\
%\thanks{A footnote to the article title}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers adhesion
between a single three-dimensional vesicle and a solid wall at $z=0$.
\todo[inline]{Need a cartoon picture in here.  Some kind of version of
the one I had for my SIAM Life Sciences Talk}
Their model uses the adhesion potential
\begin{align*}
  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
    \left(\frac{\delta}{z}\right)^2 - 2 \right],
\end{align*}
where $z$ is the distance between the solid wall and the vesicle,
$\sigma$ is the Hamaker constant, and $\delta$ is the adhesion length
scale.  We generalize this model to an unbounded suspension of vesicles.
We assume that the adhesion force applies between all pairs of points on
different vesicles, so we are interested in Hamaker constants that are
appropriate for lipid-lipid interactions. In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^2} 
  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}

@@

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}
\todo[inline]{Do the smaller reduced area doublets since the intrinsic
viscosity seemed to increase as the reduced area was decresed further}
\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
adhesion and due to the bending/tension}

@@

\section{Small Deformation Limit}
\label{sec:appendixB}
\todo[inline]{Used to validate the code/results}

>>>>

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[aps,prl,showpacs,amsmath,amssymb]{revtex4-1}

@@

\title{Hydrodynamics and rheology of adhesive vesicle doublets}
% Force line breaks with \\
%\thanks{A footnote to the article title}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers adhesion
between a single three-dimensional vesicle and a solid wall at $z=0$.
\todo[inline]{Need a cartoon picture in here.  Some kind of version of
the one I had for my SIAM Life Sciences Talk}
Their model uses the adhesion potential
\begin{align*}
  \phi(z) = \sigma\left(\frac{\delta}{z}\right)^2 \left[ 
    \left(\frac{\delta}{z}\right)^2 - 2 \right],
\end{align*}
where $z$ is the distance between the solid wall and the vesicle,
$\sigma$ is the Hamaker constant, and $\delta$ is the adhesion length
scale.  We generalize this model to an unbounded suspension of vesicles.
We assume that the adhesion force applies between all pairs of points on
different vesicles, so we are interested in Hamaker constants that are
appropriate for lipid-lipid interactions. In
Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-4 \sigma \delta^2\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^6} 
  \left(\delta^2 - \|\xx - \yy\|^2 \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}

@@

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
  \todo[inline]{Make black marks larger and reference that they come
  from Ghigliotti, Biben, Misbah 2010 JFM}
\end{figure}
\todo[inline]{Do the smaller reduced area doublets since the intrinsic
viscosity seemed to increase as the reduced area was decresed further}
\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
adhesion and due to the bending/tension}

@@

%\section{Small Deformation Analysis on a Single Vesicle in Linear Shear Flow}
%\label{sec:appendixB}
%\todo[inline]{Used to validate the code/results}
%Hydrodynamics of a single vesicle in Stokes flow has been extensively investigated. 
%In a planar shear flow, the vesicle hydrodynamics is characterized by
%excess area (reduced volume), viscosity contrast between interior and exterior fluids, and shear rate of the imposed far-field fluid flow. 
%%In addition a vesicle with a rigid particle inside is also investigated as a biological mimic of a 
%%eukaryotic cell with a nucleus that occupies nearly half of the intracellular volume \cite{Veerapaneni2011_PRL}. 
%Small-deformation analysis shows that
%a vesicle tank-treads in a planar shear flow for low viscosity contrast and shear rate. At high viscosity contrast the tank-tread (TT) dynamics transitions to tumbling (TB) \cite{Misbah2006_PRL,Vlahovska2007_PRE} ,
%and this leads to a transition in effective shear viscosity in the vesicle suspension \cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
%by direct numerical simulations \cite{GhigliottiBibenMisbah2010_JFM} and experiments \cite{KantslerSegreSteinberg2008_EPL,ZabuskySegreDeschamps2011_PoF}.
%Between TT and TB vesicle hydrodynamics, a breathing (tremble) is also observed \cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2011_JFM,SpannZhaoShaqfeh2014_PoF} to affect the effective shear viscosity in a 
%different way.
%Some of these theoretical results have inspired detailed comparison of rheology of a dilute vesicle suspension between direct numerical simulations and experiments.
%Here we follow the small-deformation analysis by Finken {\it et al.} to derive the effective shear viscosity of a dilute suspension of TT vesicle in a planar shear flow.
%The main results in the derivation carried out in the Mathematica run script (supplementary material) are summarized here.
%For the homogeneous membrane tension of an inextensible two-dimensional vesicle (with an excess length $\triangle$) under a planar shear flow we found
%\begin{equation}
%\sigma_0 = -\frac{5}{2} + 
%\end{equation}
%
%The effective shear viscosity of a single TT vesicle in a planar shear flow has been 
%
% studied and comparison between numerical simulations, small-deformation theory and experiments has been made.
%Following the asymptotic analysis by Finken {\it et al.} \cite{Finken2008_EPL} we 
%In an extensional flow (planar or uniaxial), vesicle shape dynamics
%depends sensitively on the vesicle reduced volume  and the elastic capillary number \cite{KantslerSegreSteinberg2008_PRL,ZhaoShaqfeh2013_JFM,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape and oscillatory undulation of the vesicle membrane are two examples of the complex vesicle hydrodynamics in an extensional flow.
